Climate-driven phytoplankton community variability in the Cariaco Basin, Venezuela

### 2025-05-13 agujournaltemplate.tex

\begin{figure}
\noindent\includegraphics[width=\textwidth]{fig/Figure4_ClusteringNMDS_v2.pdf}
\caption{(a) Clustering of microscopy data at the Genus level, using the binary Jaccard distance. The community for each year is binned together, to smooth out seasonal aspects. (b) Species turnover between years for annual aggregate of identified phytoplankton to a genus level. The three genera dominating the cell counts for the separate parts of cluster 1 and cluster 2 are given in order of abundance from top to bottom. (c) NMDS plot of monthly community data (cell counts) that is cube-root transformed. Stress: 0.261, 2 dimensions, converging solution. Color of dots based on which yearly cluster the monthly data is in. Vector overlay of ENVFIT shows underlying environmental variables that are co-varying with the community data.}
\label{fig:clustering}
\end{figure}

@@

>>>>

\begin{figure}
\noindent\includegraphics[width=\textwidth]{fig/Figure4_ClusteringNMDS_v2.pdf}
\caption{(a) Hierarchichal lustering by complete linkage method of microscopy cell counts at the Genus level, using the binary Jaccard distance. The community for each year is binned together, to smooth out seasonal aspects. (b) Species turnover between years for annual aggregate of identified phytoplankton to a genus level. The three genera dominating the cell counts for the separate parts of cluster 1 and cluster 2 are given in order of abundance from top to bottom. (c) NMDS plot of monthly community data (cell counts) that is cube-root transformed. Stress: 0.261, 2 dimensions, converging solution. Color of dots based on which yearly cluster the monthly data is in. Vector overlay of ENVFIT shows underlying environmental variables that are co-varying with the community data.}
\label{fig:clustering}
\end{figure}

@@

\section{Correlation of data}

\begin{figure}
\noindent\includegraphics[width=\textwidth]{fig/CorrClustSupplementalPlot_v1.pdf}
\caption{Correlation matrix with clustering of all datasets presented. Correlation was calcualted using a Spearman's rank correlation coefficient, the magnitude of the coefficient is indicated by the color of the circle. The size of the circle and significance level marking (***=p<0.001, **=p<0.01, *=p<0.05) 
for hierarchical clustering }
\label{fig:map}
\end{figure}
